Estimating Correspondences of Deformable Objects ``In-the-wild"

### 2015-11-06 contents/evaluation.tex

Cumulative Error Distributions (CED) for this experiment are shown in Figure \ref{fig:hand_benchmark} while fitting statistics are reported in Table \ref{tab:hand_benchmark}. Results show that, for this experiment, the fitting accuracy achieved by our method outperformed current state-of-the-art algorithms. In particular, our method improves performance of current best method \cite{pfister2015flowing} by a notable amount (9\% with error less than 6pt) on wrist, as well as marginal improvement on elbow estimation. Detailed statistical results please refer to supplementary material.

\begin{figure}[b!]
    \centering
    \begin{subfigure}[b]{0.23\textwidth}
            \includegraphics[width=\textwidth]{resources/HandBenchmark/wrist}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.23\textwidth}
            \includegraphics[width=\textwidth]{resources/HandBenchmark/elbow}
    \end{subfigure}
    \caption{CEDs over skeleton landmarks on BBC Pose database for experiment \ref{exp:benchmark}}
    \label{fig:hand_benchmark}
\end{figure}

@@

\subsection{Non-rigid Object Alignment In-the-wild}
\label{exp:internal}

\subsection{Annotation Correct}
\label{exp:qualitative}

>>>>

Cumulative Error Distributions (CED) for this experiment are shown in Figure \ref{fig:hand_benchmark} while fitting statistics are shown in supplementary material. Results show that, for this experiment, the fitting accuracy achieved by our method outperformed current state-of-the-art algorithms. In particular, our method improves performance of current best method \cite{pfister2015flowing} by a notable amount (9\% with error less than 6pt) on wrist, as well as marginal improvement on elbow estimation.

\begin{figure}[b!]
    \centering
    \includegraphics[width=\columnwidth]{resources/HandBenchmark/wrist}
    \\
    \includegraphics[width=0.48\columnwidth]{resources/HandBenchmark/wrist}
    \includegraphics[width=0.48\columnwidth]{resources/HandBenchmark/elbow}
    \caption{CEDs over skeleton landmarks on BBC Pose database for experiment \ref{exp:benchmark}}
    \label{fig:hand_benchmark}
\end{figure}

@@

\subsection{Non-rigid Object Alignment In-the-wild}
\label{exp:internal}
\begin{figure}[b!]
    \centering
    \begin{subfigure}[b]{0.23\textwidth}
            \includegraphics[width=\textwidth]{resources/DAAMBenchmark/face}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.23\textwidth}
            \includegraphics[width=\textwidth]{resources/DAAMBenchmark/ear}
    \end{subfigure}
    \caption{CEDs over skeleton landmarks on BBC Pose database for experiment \ref{exp:benchmark}}
    \label{fig:daam_benchmark}
\end{figure}

This experiment compares the fitting accuracy of our dAAMs versus the one of classic AAM on the problem of nonrigid face and ear alignment in-the-wild.

For face experiment, both models were built using the 811 training images of the Labelled
Faces Parts in-the-Wild (LFPW) \cite{Asthana2014} database. Classic AAM were built from 68 point landmark annotations using the standard procedure described in \cite{Cootes2001,Matthews2004}; piecewise affine was used as their motion model. Our dAAMs were built as the pipeline proposed. Results for this experiment are reported over the 224 testing images of the LFPW database using again 68 point ground truth landmark annotations. For this experiment, we report results using pixels intensities (INT) for both models.

For ear experiment, we studied the feasibility of building and fitting statistical deformable models that capture the variability of the human ear. To this end, we collected 605 high resolution images of ears in unconstrained scenarios and annotated them using both a newly defined 55 point annotation scheme for ears and the curve annotations proposed in this paper. Examples of these two type of ear annotations are shown in Figure \ref{fig:intro}. We randomly split the previous database into two disjoint sets of training (500) and testing (105) images. Both models were built using the 500 images training set and their fitting accuracy evaluated on the 105 images of the testing set. Note here that we used the same procedures to build the models as for faces and same error metric for evaluation.

CED Curves for this experiment are shown in Figure \ref{fig:daam_benchmark}. We can readily observe that the accuracy achieved by ear models, in terms of the previous normalized point-to-point error measure, is lower than the one achieved by face models. This result is expected due to the more complex structure of the ear shape. Through visual inspection we determined that fitting errors below 0.1 for ears typically look plausible under the previous error measure where fitting errors below 0.6 for faces. Results show that, for this experiment, the fitting accuracy achieved by our dAAMs is marginally better to the one achieved by classic AAMs using intensity representations. In fact, classic AAM fail to improve the accuracy of the original initialisation on ears. Therefore the propose pipeline is capable of dealing with the complex structure of non-rigid shapes and learn dAAMs from simple curve line annotations that can compete and even surpass (in the case of a simple pixel intensity image representation) classic AAM, build from carefully annotated point landmarks, is quite remarkable.

\subsection{Annotation Correction}
\label{exp:qualitative}
